Dependent Object Types

### 2012-09-03 doc/candidacy/slides.tex
selected papers

\inputminted[frame=lines,fontsize=\footnotesize]{scala}{intro.scala}

>>>>

\inputminted[frame=lines,fontsize=\footnotesize]{scala}{intro.scala}
\end{frame}

\begin{frame}{Selected Papers}
\begin{enumerate}
\item {\it A Type-Theoretic Approach to Higher-Order
  Modules with Sharing}\\{\footnotesize by Robert Harper and Mark
  Lillibridge}\begin{itemize}
\item calculus for modules in the ML tradition
\item modules are first-class values
\end{itemize}
\item {\it Tribe: a simple virtual class calculus}\\
  {\footnotesize by Dave Clarke, Sophia Drossopoulou, James Noble and Tobias
  Wrigstad}\begin{itemize}
\item calculus for virtual classes
\end{itemize}
\item {\it A Nominal Theory of Objects with Dependent
  Types}\\{\footnotesize by Martin Odersky, Vincent Cremet, Christine R{\"o}ckl and
  Matthias Zenger}\begin{itemize}
\item calculus unifying advanced object-oriented and module systems
\item foundation for Scala
\end{itemize}
\end{enumerate}
\end{frame}
